Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-05 WSSSPE3/report/wg_appendix_metrics.tex
small edits

Gabrielle Allen \footnote{email: \href{mailto:gdallen@illinois.edu}{gdallen@illinois.edu}} will serve as the point of contact for this working group.

@@

The following summary of the group’s discussion represents the Useful Metrics for Scientific Software working group’s discussion during the WSSSPE3 workshop. The group discussion began by agreeing on the common purpose of creating a set of guidance giving examples of specific metrics for the success of scientific software in use, why they were chosen, what they are useful to measure, and any challenges and pitfalls; then publish this as a white paper.  The group discussed many questions related to useful metrics for scientific software as follows:

@@

The following opportunies, challenges, and obstacles were discussed:

@@

\item
We don’t know if there is a common set of metrics

@@

\begin{enumerate}
\item
October – November 2015: IRB paperwork as appropriate completed (Gabrielle Allen and Emily Chen)

\item
October – December 2015: Draft white paper sections 1-3 (the paper outline has initial writing assignments)

\item
October – December 2015: Run surveys and collect information

\begin{enumerate}
\item
        Piggy back on planning for 2016 NSF SI2 PIs meeting to be held Feb 16-17, 2016
\end{enumerate}

\item
January – February 2016: Analyze results of data collection from projects

\item
March – April 2016: Draft sections 4-7 of the white paper

@@

\item
May – June 2016: Get initial feedback from members of the community and revise

@@

\item
Est. Sept – Oct 2016: Responses to white paper submitted to WSSSPE4

>>>>

Gabrielle Allen\footnote{email: \href{mailto:gdallen@illinois.edu}{gdallen@illinois.edu}} will serve as the point of contact for this working group.

@@

The following summary of the group's discussion represents the Useful Metrics for Scientific Software working group's discussion during the WSSSPE3 workshop. The group discussion began by agreeing on the common purpose of creating a set of guidance giving examples of specific metrics for the success of scientific software in use, why they were chosen, what they are useful to measure, and any challenges and pitfalls; then publish this as a white paper.  The group discussed many questions related to useful metrics for scientific software as follows:

@@

The following opportunities, challenges, and obstacles were discussed:

@@

\item
We don't know if there is a common set of metrics

@@

\begin{enumerate}
\item
October -- November 2015: IRB paperwork as appropriate completed (Gabrielle Allen and Emily Chen)

\item
October -- December 2015: Draft white paper sections 1-3 (the paper outline has initial writing assignments)

\item
October -- December 2015: Run surveys and collect information

\begin{enumerate}
\item
        Piggyback on planning for 2016 NSF SI2 PIs meeting to be held Feb 16-17, 2016
\end{enumerate}

\item
January -- February 2016: Analyze results of data collection from projects

\item
March -- April 2016: Draft sections 4-7 of the white paper

@@

\item
May -- June 2016: Get initial feedback from members of the community and revise

@@

\item
Est. Sept -- Oct 2016: Responses to white paper submitted to WSSSPE4
